Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-12 paper.tex
Updates to mutation illustration

% Franz
\affil[1]{Mathematical and Computational Population Genetics, University of T\"ubingen}
% Gertjan, Konrad
\affil[2]{Institute of Evolutionary Biology, The University of Edinburgh}
% Daniel
\affil[3]{Khoury College of Computer Sciences, Northeastern University}
% Graham
\affil[4]{Lundbeck GeoGenetics Centre, Globe Institute, University of Copenhagen}
% Aaron
\affil[5]{Department of Integrative Biology, University of Wisconsin--Madison}
% Georgia
\affil[6]{Melbourne Integrative Genomics, School of Mathematics and Statistics,
    University of Melbourne}
% Jerome, Yan, Wilder, Joe
\affil[7]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
    University of Oxford}

@@

\textbf{Keywords:} Coalescent simulation, Python, ancestral recombination graphs

@@

\begin{figure}
    \includegraphics{illustrations/unmutated_tree}
    \includegraphics{illustrations/mutated_tree}
    \caption{
        \label{fig-mutated-trees}
        Visualisation of the separation between ancestry and mutation simulation:
        \texttt{sim\_ancestry} produces ancestry
        (\textbf{left;} shown are two trees along a 1Kb chunk of genome
        relating 200 samples),
        and \texttt{sim\_mutations} adds mutations
        (\textbf{right;} fourteen nucleotide mutations have been added).
        Graphics produced with \tskit's \texttt{draw\_svg} method.
        \plrcomment{TODO: fix up the axis labels, if we like this figure?}
        \jkcomment{Why 200 samples? Seems like far too many to me, how about 5?}
        \grgcomment{Add \texttt{sim\_ancestry} and \texttt{sim\_mutations} as subfigure titles?}
    }
\end{figure}

@@

% If we interpret an ARG as being a graph describing genetic
% ancestry, then clearly a

% \jkcomment{This paragraph has been copied from the previous
% version of the Tree Sequences section. Update and merge in here
% as appropriate.}
% The tree sequence encoding of ancestry as a set of nodes and edges
% as just described, is equivalent to a graph in which edges
% are annotated with a set of disjoint genomic intervals.
% This is closely related to the Ancestral Recombination Graph (ARG),
% a term that is often loosely understood
% to mean some representation of genetic
% ancestry as a graph~\citep[e.g.][]{mathieson2020ancestry}.
% In this sense a succinct tree sequence \emph{is} an ARG.
% More technically, an ARG is a particular
% Fepresentation of genetic ancestry as a graph based on the
% flow of ancestral material through recombination and common
% ancestor events~\citep{griffiths1991two,griffiths1997ancestral}.
% In this sense, tree sequences can be used to \emph{encode}
% ARGs without loss of information (although
% the default minimal tree sequence encoding is
% much more concise; see the \nameref{sec-arg} section).
% It should be noted that, despite standardisation
% efforts~\citep{cardona2008extended,mcgill2013graphml}, there is
% no shared format for interchanging ARG data, and no supporting software
% libraries.

>>>>

% Franz
\affil[1]{Cluster of Excellence ``Controlling Microbes to Fight Infections'',
Mathematical and Computational Population Genetics, University of T\"ubingen}
% Gertjan, Konrad
\affil[2]{Institute of Evolutionary Biology, The University of Edinburgh}
% Daniel
\affil[3]{Khoury College of Computer Sciences, Northeastern University}
% Graham
\affil[4]{Lundbeck GeoGenetics Centre, Globe Institute, University of Copenhagen}
% Aaron
\affil[5]{Department of Integrative Biology, University of Wisconsin--Madison}
% Georgia
\affil[6]{Melbourne Integrative Genomics, School of Mathematics and Statistics,
    University of Melbourne}
% Jerome, Yan, Wilder, Joe
\affil[7]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
    University of Oxford}

@@

\textbf{Keywords:} Coalescent simulation, Python, Ancestral Recombination Graphs

@@

\begin{figure}
    \includegraphics{illustrations/mutated_tree}
    \caption{
        \label{fig-mutated-trees}
        Visualisation of the separation between ancestry and mutation simulation:
        \texttt{sim\_ancestry} produces ancestry
        (\textbf{left;} shown are two trees along a 1Kb chunk of genome
        relating 200 samples),
        and \texttt{sim\_mutations} adds mutations
        (\textbf{right;} fourteen nucleotide mutations have been added).
        Graphics produced with \tskit's \texttt{draw\_svg} method.
        \plrcomment{TODO: fix up the axis labels, if we like this figure?}
        \jkcomment{Why 200 samples? Seems like far too many to me, how about 5?}
        \grgcomment{Add \texttt{sim\_ancestry} and \texttt{sim\_mutations} as subfigure titles?}
    }
\end{figure}

@@
